\mytitle

### 2016-10-09 pdocs/thesis/article-section-3.tex
Finetuning of article -new pictures to charpy

@@

Figure \ref{fig:charpy} shows screenshot from simulation.
\begin{figure}[htb!]
\centering
\includegraphics[height=8cm]{figs/article-charpy}
\caption{Simulation of Charpy impact test}
\label{fig:charpy}
\end{figure}

>>>>

Figure \ref{fig:charpy-series} shows three detailed pictures from simulation.
Left picture shows early phase of simulation. In middle picture hammer has not yet collided with specimen.
In right picture specimen is bending.

\begin{figure}[htb!]
\centering
\includegraphics[height=3cm]{figs/article-charpy-1}
\includegraphics[height=3cm]{figs/article-charpy-2}
\includegraphics[height=3cm]{figs/article-charpy-3}
\caption{Detailed pictures from simulation of Charpy impact test}
\label{fig:charpy-series}
\end{figure}

@@

Figure \ref{fig:charpy} shows overview from simulation as specimen is going between supports.

\begin{figure}[htb!]
\centering
\includegraphics[height=8cm]{figs/article-charpy}
\caption{Overview of simulation of Charpy impact test}
\label{fig:charpy}
\end{figure}
